---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# group05pkg

<!-- badges: start -->
<!-- badges: end -->

The goal of group05pkg is to aid in creating a classification analysis project
end to end. It has functions that read in the data, clean the data, plot the 
data, and train/test classification models on the data. It also contains functions
that can test the model's accuracy.

## Installation

You can install the development version of group05pkg from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("DaliaAh/dsci-310-group-05-pkg")
```

## Example

This is a basic example which shows you how to train a classification model:

```{r example}

```

You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this. You could also use GitHub Actions to re-render `README.Rmd` every time you push. An example workflow can be found here: <https://github.com/r-lib/actions/tree/v1/examples>.

You can also embed plots, for example:

```{r pressure, echo = FALSE}
plot(pressure)
```

In that case, don't forget to commit and push the resulting figure files, so they display on GitHub and CRAN.
