---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# group05pkg

<!-- badges: start -->
[![codecov](https://codecov.io/github/DaliaAh/dsci-310-group-05-pkg/branch/main/graph/badge.svg)](https://app.codecov.io/github/DaliaAh/dsci-310-group-05-pkg)
[![test-coverage](https://github.com/DaliaAh/dsci-310-group-05-pkg/actions/workflows/test-coverage.yaml/badge.svg)](https://github.com/DaliaAh/dsci-310-group-05-pkg/actions/workflows/test-coverage.yaml)
[![R-CMD-CHECK](https://github.com/DaliaAh/dsci-310-group-05-pkg/workflows/R-CMD-check/badge.svg)](https://github.com/DaliaAh/dsci-310-group-05-pkg/actions/workflows/check-release.yaml)

<!-- badges: end -->

The goal of group05pkg is to aid in creating a classification analysis project
end to end. It includes functions that create training and test sets, clean the data, plot the data, create specification, recipe and v-fold cross-validation objects to use in a  classification model.

## Package Website

You can visit the package website [here](https://dsci-310.github.io/dsci-310-group-05-pkg/).

## Installation

You can install the development version of group05pkg from [GitHub](https://github.com/DaliaAh/dsci-310-group-05-pkg) with:

``` r
# install.packages("devtools")
devtools::install_github("DaliaAh/dsci-310-group-05-pkg")
```

### Functions Included:

- `split_dataset()`
- `wrangle_training_data()`
- `horizontal_hist()`
- `scatterplot()`
- `create_knn_spec()`
- `create_recipe()`
- `create_vfold()`

## Examples

Here are some basic examples that show how to use the functions in this package:

```{r example}
library(group05pkg)
```

1. Using `split_dataset` you can split a dataset into training and testing sets based on a strata variable. Here we use `iris` dataset.

```{r split_dataset, echo=TRUE, error=FALSE, message=FALSE, warning=FALSE}
result<-split_dataset(iris, "Species", "Sepal.Length")
training_set <- result[[1]]
test_set <- result[[2]]
head(training_set)
dim(training_set)

head(test_set)
dim(test_set)
```

2. Using `wrangle_training_data()`, you can  group training data by predictor and strata_variables and add a group_labels column. Here we are using a dummy training data to pass into our function.

```{r wrangle_training_data, echo=TRUE, error=FALSE, message=FALSE, warning=FALSE}
# Given a dummy training  data called training_data
training_data <- data.frame(
  col1 = c("yes", "no", "yes", "no"),
  col2 = c("yes", "yes", "no", "no"),
  col3 = c(2,4, 6, 8)
)

label<- c("Label 1")

wrangled<- wrangle_training_data(training_data, col1, col2 , label)
wrangled
```

3. Using `horizontal_hist` function we can build a horizontal histogram that will help understand the pattern between two variables. Here we are using `mtcars` dataset again.

```{r horizontal_hist, echo=TRUE, error=FALSE, message=FALSE, warning=FALSE}
horizontal_hist(mtcars, cyl, disp, "cyl",
   "disp", "cyl vs disp",
   plot_width = 2, plot_height = 3
 )
```

4. Using `scatterplot` function we can build a scatter plot to help understand the relationship between two variables. Here we are using `mtcars` dataset.

```{r scatterplot, echo=TRUE, error=FALSE, message=FALSE, warning=FALSE}
scatterplot(mtcars, mpg, cyl, disp, "mpg",
   "cyl", "disp",
   "mpg vs. cyl",
   plot_width = 2, plot_height = 3)
```

5. Using `create_knn_spec` we can create a specification object where we can specify the weight function. We can use the specification object created in training k-nearest neighbor models.

```{r create_knn_spec, echo=TRUE, error=FALSE, message=FALSE, warning=FALSE}
create_knn_spec("rectangular")
```

6. Using `create_recipe` we can create a recipe object by specifying the dataset and response variable. This object can be used in a modelling workflow. Here we use `iris` dataset.

```{r create_recipe, echo=TRUE, error=FALSE, message=FALSE, warning=FALSE}
create_recipe(iris, "Species")
```

7. Using `create_vfold` we can create a v-fold cross-validation object by specifying the dataset, the number of folds, and a strata variable. This object then can to used in a modelling workflow. Here we use `iris` dataset.

```{r create_vfold, echo=TRUE, error=FALSE, message=FALSE, warning=FALSE}
create_vfold(iris, 5, "Species")
```

## Contributing

Thank you for taking the time to contribute to the `group05pkg`! We welcome contributions from anyone who is interested in improving the project. Please use your best judgment, and feel free to propose any changes you deem appropriate in a pull request. Please refer to [CONTRIBUTING](https://github.com/DaliaAh/dsci-310-group-05-pkg/blob/main/CONTRIBUTING.md) and [CODE_OF_CONDUCT](https://github.com/DaliaAh/dsci-310-group-05-pkg/blob/main/CODE_OF_CONDUCT.md) for more information.


## License
This project is offered under the [Attribution 4.0 International (CC BY 4.0) License](https://creativecommons.org/licenses/by/4.0/). The software provided in this project is offered under the [MIT open source license](https://opensource.org/license/mit/) . See the [license file](https://github.com/DaliaAh/dsci-310-group-05-pkg/blob/main/LICENSE.md) for more information.
