---
title: "Introduction to group05pkg"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{package_name-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  comment = "#>",
  warning = FALSE,
  message = FALSE
)
```

```{r load_all, include=FALSE}
devtools::load_all(".")
```

Data analysis requires a structured approach that involves cleaning, wrangling,
modeling, and evaluating the performance of different models. However, these 
tasks can be challenging, and traditional approaches of writing large code chunks
to run this kind of analysis can be time-consuming and error-prone.

**This is where the package group05pkg comes in!**

It provides a set of easy-to-use functions that simplify the process of running
a classification analysis such as:

- Split your data set into train and test
- Create the components of a classification model such as the KNN specification,
a recipe, cross-validation folds, and a grid of hyperparameters that can be used
to tune the performance of a model.
- Evaluate the accuracy of your model. 
- Plot histograms and scatterplots to visualize your analysis. 

This document introduces you to group05pkg’s basic set of tools, and shows you 
how to apply them to run a classification analysis.

## Data: iris 
To explore the package, we will be using the iris data set. This data set contains
`150 rows` and `5 columns`. To read the iris data set documentation, you can check `?iris`

```{r setup}
library(group05pkg)
dim(iris)
head(iris)
```
