---
title: "Introduction to group05pkg"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{package_name-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  comment = "#>",
  warning = FALSE,
  message = FALSE
)
```

```{r load_all, include=FALSE}
devtools::load_all(".")
```

Data analysis requires a structured approach that involves cleaning, wrangling,
modeling, and evaluating the performance of different models. However, these 
tasks can be challenging, and traditional approaches of writing large code chunks
to run this kind of analysis can be time-consuming and error-prone.

**This is where the package group05pkg comes in!**

It provides a set of easy-to-use functions that simplify the process of running
a classification analysis such as:

- Split your data set into train and test
- Create the components of a classification model such as the KNN specification,
a recipe, cross-validation folds, and a grid of hyperparameters that can be used
to tune the performance of a model.
- Evaluate the accuracy of your model. 
- Plot histograms and scatterplots to visualize your analysis. 

This document introduces you to group05pkg’s basic set of tools, and shows you 
how to apply them to run a classification analysis.

## Data: drug_consumption
To explore the package, we will be using the `drug_consumption` data set.This data
set has `1884 rows` and `32 columns`.

```{r setup, include = FALSE}
library(group05pkg)
```

```{r drug-consumption}
drug_consumption <- readr::read_csv("https://archive.ics.uci.edu/ml/machine-learning-databases/00373/drug_consumption.data")

colnames(drug_consumption) <- c(
  "ID", "Age", "Gender", "Education", "Country", "Ethnicity",
  "Nscore", "Escore", "Oscore", "Ascore", "Cscore",
  "Impulsive", "SS", "Alcohol", "Amphet", "Amyl", "Benzos",
  "Caff", "Cannabis", "Choc", "Coke", "Crack", "Ecstasy",
  "Heroin", "Ketamine", "Legalh", "LSD", "Meth", "Mushrooms",
  "Nicotine", "Semer", "VSA"
)
head(drug_consumption)
```

## Functions

We can break down our functions into 3 different groups: 

- EDA 
- Visualizations
- Classification Models

### Classification Models 

#### 1. Create knn specification with `create_knn_spec()`

create_knn_spec() is a function in R that creates a specification object for 
k-nearest neighbor models. The function takes one argument, weight_func, which
is a string that specifies the weight function to use in the model.

The function creates a specification object using the nearest_neighbor() function
from the parsnip package. The weight_func argument is used to set the weight 
function in the specification object.

The neighbors parameter is set as a tuning parameter using the tune() function. 
This means that the number of neighbors will be selected based on the best 
performance during model training.

The specification object is then set to use the kknn engine and set to 
classification mode. Finally, the function returns the specification object.

To use the create_knn_spec() function, you simply provide a string for the 
weight_func argument. For example, to create a specification object with a weight 
function of "triangular", you can use the following code:

```{r create-knn-spec}
knn_spec <- create_knn_spec("rectangular")
knn_spec
```
#### 2. Create knn specification with `create_recipe()`

